What is disputed on the web?

### 2010-02-24 papers/wicow_claimfinder/claimfinder_final.tex
Starting work on camera-ready version of the WICOW paper
Making changes requested by reviewers and updating for a bigger data set

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we use. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed unambigous claim.

@@

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approximately 1.1 million strings that our classifier believes are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

It is useful to be able to update our corpus as new pages appear on the web without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

@@

Whether a claim is unambiguous is ofter subjective. For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''. When manually judging claims, we considered a claim to be unambiguous if an average person would be pretty sure what the claim meant without knowing its context.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5.pdf}
	\caption{Number of claims containing a particular noun on January 10th of any particular year}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 1.1 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analyzed the distribution of noun frequencies in claims made on January 10th of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even these nouns prove to be quite interesting.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israe:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words in the cluster. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alledged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed). Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.

@@

Our data set currently includes approximately 1.1 million records. In the future we intend to expand this by several orders of magnitude.

>>>>

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we use. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed unambiguous claim.

@@

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 31st 2010, and pages written between January 1st and January 31st of every year from 2000 to 2010. This amounts to approximately 3.6 million strings that our classifier believes are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

It is useful to be able to update our corpus as new pages appear on the web without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 10 2010''}.

@@

Whether a claim is unambiguous is often subjective. For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''. When manually judging claims, we considered a claim to be unambiguous if an average person would be pretty sure what the claim meant without knowing its context.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5_bigger.pdf}
	\caption{Number of claims containing a particular noun on January 10th of any particular year}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 6.1 million text strings, of which 3.6 million were identified by our classifier as being unambiguous disputable claims. This does not mean that there are 3.6 million distinct beliefs that are disputed; many of the claims in our corpus are repeating claims made elsewhere in the corpus.

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analyzed the distribution of noun frequencies in claims made between January 1st and January 31st of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the noisy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even these nouns prove to be quite interesting.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections. We believe that most of the mentions of Obama before 2004 are due to date classification errors.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} Spikes seem to correspond to the 2009 Gaza conflict and the 2006 Lebanon conflict.
\end{itemize}

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words in the cluster. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alleged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed). Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.

@@

Our data set currently includes approximately 3.6 million records. In the future we intend to expand this by several orders of magnitude.
